Jug: Software for Reproducible Computation

### 2011-11-28 paper.tex
MIN Minor phrasing fixes

\subsection{Development Support}

@@

@@

\section{Discussion}
Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication (in fact, when it
comes to communication other tools might be better targetted as they combine
written exposition with computer code). While it still possible to make errors
(for example, by changing the code but neglecting to invalidate the results),
jug improves the pipeline development experience and makes the programming
researcher more productive.

>>>>

\subsection{Software Development With Jug}

@@

This is a feature which can be used to debug one's own code or to explore the
results of a computation by others.

@@

\section{Discussion}
Unlike most previous tools for reproducible research, jug focuses on the
development of the computation as much as its communication (in fact, when it
comes to communication other tools might be better suited as they combine
written exposition with computer code). While it still possible to make errors
(for example, by changing the code but neglecting to invalidate the results),
jug improves the pipeline development experience and makes the programming
researcher more productive.
